Diffantom: whole-brain diffusion MRI phantoms derived from real datasets of the \acrlong{hcp}

### 2015-08-26 paper/main.tex
fix typo in title
fixes #25

\title[Diffantom]{Diffantom: a whole-brain diffusion MRI phantoms derived from real datasets of the \acrlong{hcp}}

@@

\noindent\textbf{\textit{Diffusion signal generation\textcolon}\label{sec:data_dwi}} %
Once a microstructural model of the volume has been synthesized, a map of \glspl{fodf} is computed using spherical
  convolution of the single fiber response and the fiber orientation maps $\{\mathbf{V}_i\}$, weighted by the
  corresponding fiber-fractions $\{F_i\}$.
A close-up showing how the \glspl{fodf} map looks is presented in \autoref{fig:figure1}-B.
The single fiber response is a Gaussian diffusion tensor with axial symmetry and eigenvalues $\lambda_1=$ 2.2\e{-3}
  \diffunits{} and $\lambda_{2,3}=$ 0.2\e{-3} \diffunits{}.
The resulting \glspl{fodf} map is then combined with the free- and hindered-diffusion compartments corresponding to $\{T_j\}$.
The free-diffusion compartment corresponds to the \gls*{csf} fraction map $T_4$ and is modeled with isotropic
  diffusivity $D_{CSF}$ of 3.0\e{-3} \diffunits{}.
The hindered-diffusion compartments correspond to $\{T_1,T_2,T_3\}$ and are also modeled with isotropic diffusivity
  $D_{WM} =$ 2.0\e{-4}, $D_{cGM} =$ 7.0\e{-4} and $D_{dGM} =$ 9.0\e{-4}, respectively [\diffunits{}].
All these values for diffusivity (and the corresponding to the single-fiber response) can be modified by the user with
  custom settings.
The restricted- and hindered- compartments are then fed into \emph{Phantomas} \citep{caruyer_phantomas_2014}
  and the final \gls*{dmri} signal is obtained.
By default, diffusion data are generated using a scheme of 100 directions distributed in one shell with uniform
  coverage \citep{caruyer_design_2013}.
Custom one- or multi-shell schemes can be generated supplying the tables of corresponding vectors and $b$-values.
Rician noise is also included in \emph{Phantomas}, and the \gls*{snr} can be set by the user.
The default value for \gls*{snr} is preset to 30.0.

>>>>

\title[Diffantom]{Diffantom: whole-brain diffusion MRI phantoms derived from real datasets of the \acrlong{hcp}}

@@

\noindent\textbf{\textit{Diffusion signal generation\textcolon}\label{sec:data_dwi}} %
Once a microstructural model of the subject has been synthesized, the fiber orientation maps $\{\mathbf{V}_i\}$
  are weighted by the fiber-fraction maps $\{F_i\}$ and projected onto a continuous representation of
  the \glspl{fod}.
A close-up showing how the \glspl{fod} map looks is presented in \autoref{fig:figure1}B.
The single fiber response is a Gaussian diffusion tensor with axial symmetry and eigenvalues $\lambda_1=$ 2.2\e{-3}
  \diffunits{} and $\lambda_{2,3}=$ 0.2\e{-3} \diffunits{}.
The resulting \glspl{fod} map is then combined with the free- and hindered-diffusion compartments corresponding to $\{T_j\}$.
The free-diffusion compartment corresponds to the \gls*{csf} fraction map $T_4$ and is modeled with isotropic
  diffusivity $D_{CSF}$ of 3.0\e{-3} \diffunits{}.
The hindered-diffusion compartments correspond to $\{T_1,T_2,T_3\}$ and are also modeled with isotropic diffusivity
  $D_{WM} =$ 2.0\e{-4}, $D_{cGM} =$ 7.0\e{-4} and $D_{dGM} =$ 9.0\e{-4}, respectively [\diffunits{}].
All these values for diffusivity (and the corresponding to the single-fiber response) can be modified by the user with
  custom settings.
The restricted- and hindered- compartments are then fed into \emph{Phantomas} \citep{caruyer_phantomas_2014}
  and the final \gls*{dmri} signal is obtained.
By default, diffusion data are generated using a scheme of 100 directions distributed in one shell with uniform
  coverage \citep{caruyer_design_2013}.
Custom one- or multi-shell schemes can be generated supplying the tables of corresponding vectors and $b$-values.
Rician noise is also included in \emph{Phantomas}, and the \gls*{snr} can be set by the user.
The default value for \gls*{snr} is preset to 30.0.
